A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-03 paper/paper.Rnw
Add relevant parts of CC conclusion

<<>>=
img_names <- dfunion$filename %>% basename() %>% as.vector

@@

@@

>>>>

<<brand-plots>>=
img_names <- dfunion$filename %>% basename() %>% as.vector

@@

The goal of this research was to develop a method to automatically identify geometric class characteristics of shoe outsoles. Such a method takes the ``impossible" problem of quantifying outsole features in a given population and lays the groundwork for a tractable solution. A set of geometric class characteristics was defined to both broadly classify a large variety of shoes and to narrow down similarity into a manageable number and type of features for further use in a shoeprint analysis. The final set of features used in this research achieves both goals quite well, and has potential for much finer-grained analysis when recognized features are combined with spatial information and relationships.

CoNNOR was developed using the convolutional base of VGG16 and a newly trained classifier/head to identify the defined set of geometric features. After training, CoNNOR performs well on the data provided. In general, the model is able to identify many well-defined geometric shapes in the images both consistently and accurately. The prediction accuracy of this model provides the ability to compute statistics for the frequency of given features in a well-defined population.

@@

Although CoNNOR performs well in its current state, there are still a number of ways to potentially improve prediction accuracy. For one, it is clear from Section~\ref{sec:model-consistency} that image contrast still plays a large role in how well the model classifies the geometric shapes present. Thus, exploring methods of color correction, such as histogram normalization, may prove useful for eliminating the effect of contrast on predictions. Geometric features are also relatively simple with respect to the features that are being detected by the final convolutional block of VGG16, as in \autoref{fig:vgg16layers}; it is quite possible that prediction accuracy could improve by directly classifying the features that are output by the fourth block, rather than using the full convolutional base.
